### 2015-05-14 paper.tex
some cleanup

Consider that $T$ contains the inner ring of some $C^*_i$ (which was established above). We show here that all points in $T$ are within $\frac{\beta\text{OPT}}{2|C^*_i|}$ of $c_i^*$, $T \cup B(T)$ are contained in $C_I^*$ and that no other component contains inner ring points from $C^*_i$.

@@

Because all points in $T$ are sufficiently close to $C_i^*$ there are at most $|C_i^*|$ in $T$, and so $s < 2|C_i^*|$. All inner ring points are at most $\frac{\beta\text{OPT}}{4|C^*_i|} < 2r$ away from any other point, requiring all points not in $T$ be added to $B(T)$. Therefor no other component can contain inner ring points for $C_*^i$.

@@

In order to show this we will compare the total cost of clusters $\mathcal{C}$ Derived by $T_1, ..., T_k$ with those of $\mathcal{C}^*$. We know that the expensive clusters $C_i$ have centers $c_i^*$, and so its total cost will not exceed $\text{OPT}_i$.

The cost of a cheap cluster is $\sum\limits_{x\in T\cup B(T)}d(x, c_i) + \sum\limits_{x \in C_i^* and x\notin T\cup B(T)}d(x, c_i)$. Because all points in the first term are in the innter ring, that includes the center, so $\sum\limits_{x\in T\cup B(T)}d(x, c_i) \leq \sum\limits_{x\in T\cup B(T)}d(x, c^*_i)$. We must show the error in $\sum\limits_{x \in C_i^* and x\notin T\cup B(T)}d(x, c_i)$ is bounded by $(1+\epsilon)$.

@@

Thus, the runtime for the entire algorithm is $O((n^2 + nk)k^{O(\frac{1}{\beta})} + n^3)$.  However, this is only for each time the algorithm is run.  In general, the algorithm must be run once for each possible guess of the expensive clusters, using a brute-force approach.  This requires $n^{O(\frac{1}{\beta e})}$ iterations.  Thus, the overall runtime is $O(((n^2 + nk)k^{O(\frac{1}{\beta})}+n^3)n^{O(\frac{1}{\beta e})}) = O(n^{O(1/\beta\epsilon)}k^{O(1/\beta)}$ .

@@

We define $w(x)$ to be the distance from a point $x$ to it's closest cluster center, and $w_2(x)$ to be the distance to the second closest center. Let $w = \frac{\text{OPT}}{n}$ and $d_crit = 2\frac{\alpha w}{10 \epsilon}$. Let $X_i$ be the set of all points in $C_i^*$ for which $w(x) < d_crit$ and $w_2(x) - w(x) \geq 5d_crit$. Intuitively the points in $X_i$ are those which are strongly in $C_i^*$, and so moving them to the second closest cluster is expensive.

>>>>

Consider that $T$ contains the inner ring of some $C^*_i$ (which was established above). We show here that all points in $T$ are within $\frac{\beta\text{OPT}}{2|C^*_i|}$ of $c_i^*$, $T \cup B(T)$ are contained in $C_i^*$ and that no other component contains inner ring points from $C^*_i$.

@@

Because all points in $T$ are sufficiently close to $C_i^*$ there are at most $|C_i^*|$ points in $T$, and so $s < 2|C_i^*|$. All inner ring points are at most $\frac{\beta\text{OPT}}{4|C^*_i|} < 2r$ away from any other point, requiring all points not in $T$ be added to $B(T)$. Therefor no other component can contain inner ring points for $C_i^*$.

@@

In order to show this we will compare the total cost of clusters $\mathcal{C}$ Derived by $T_1, ..., T_k$ with those of $\mathcal{C}^*$.

 We know that each expensive cluster $C_i$ has centers $c_i^*$, and so its total cost will not exceed $\text{OPT}_i$.

The cost of a cheap cluster is $\sum\limits_{x\in T\cup B(T)}d(x, c_i) + \sum\limits_{x \in C_i^* and x\notin T\cup B(T)}d(x, c_i)$. Because all points in the first term are in the inner ring, that includes the center, so $\sum\limits_{x\in T\cup B(T)}d(x, c_i) \leq \sum\limits_{x\in T\cup B(T)}d(x, c^*_i)$. We must show the error in $\sum\limits_{x \in C_i^* and x\notin T\cup B(T)}d(x, c_i)$ is bounded by $(1+\epsilon)$.

@@

Thus, the runtime for the entire algorithm is $O((n^2 + nk)k^{O(\frac{1}{\beta})} + n^3)$.  However, this is only for each time the algorithm is run.  In general, the algorithm must be run once for each possible guess of the expensive clusters, using a brute-force approach.  This requires $n^{O(\frac{1}{\beta e})}$ iterations.  Thus, the overall runtime is $O(((n^2 + nk)k^{O(\frac{1}{\beta})}+n^3)n^{O(\frac{1}{\beta e})}) = O(n^{O(1/\beta\epsilon)}k^{O(1/\beta))}$ .

@@

We define $w(x)$ to be the distance from a point $x$ to it's closest cluster center, and $w_2(x)$ to be the distance to the second closest center. Let $w = \frac{\text{OPT}}{n}$ and $d_crit = 2\frac{\alpha w}{10 \epsilon}$. Let $X_i$ be the set of all points in $C_i^*$ for which $w(x) < d_{crit}$ and $w_2(x) - w(x) \geq 5d_{crit}$. Intuitively the points in $X_i$ are those which are strongly in $C_i^*$, and so moving them to the second closest cluster is expensive.
